Vagueness, Noise, and Signaling

### 2015-10-05 paper/version_04/paper.tex
Fixed references to Appendix.

@@

  \caption{A round of play in a sim-max game: Nature (N) chooses a state $\mystate{1}$ with
    probability $\Pr(\mystate{1})$; a sender (S) selects a message
    $\messg = \Spure(\mystate{1})$ determined by his pure strategy $\Spure$; a receiver (R)
    selects a state $\mystate{2} = \Rpure(\messg)$ determined by her pure strategy
    $\Rpure$. Payoff for both sender and receiver is given by
    $\Utils(\mystate{1}, \mystate{2})$.}
  \label{fig:sim-max-illustration}
\end{figure}

Formally, a sim-max game consists of a set of states $\States$, a set of messages $\Messgs$ typically with much
fewer messages than states, a probability distribution $\Pr \in \Delta(\States)$ such that
$\Pr(\state)$ gives the probability that state $\state$ occurs, a similarity metric\footnote{A
  metric is a function of distance between any two points in a given space. It should satisfy
  certain axioms that ensure behavior that one would intuitively expect from the words
  ``similarity'' and ``distance'' alone, but these details do not matter for the purposes of
  this paper.}
  % : similarity should always be non-negative, zero only for the distance
  % between an element and itself, symmetric, and satisfy the triangle inequality that
  % $\similarity(x,z) \le \similarity(x,y) + \similarity(y,z)$
on states $\similarity \mycolon \States \times \States \rightarrow \mathds{R}$ such that
$\similarity(\mystate{1}, \mystate{2})$ is the (perceptual) similarity between $\mystate{1}$
and $\mystate{2}$, and a utility function $\Utils \mycolon \States \times \States \rightarrow
\mathds{R}$ such that $\Utils(\mystate{1}, \mystate{2})$ is the payoff for sender and receiver
for a play with actual state $\mystate{1}$ and receiver interpretation $\mystate{2}$. We
identify the receiver's acts with the states of the world, so that the game is one of guessing
the actual state, so to speak. The utility function should be a monotonically decreasing
function of similarity.
In its original formulation, a sender's behavior is represented by a pure strategy $\Spure \in \Messgs^\States$ which associates states to messages (given a state $\state \in \States$ which message $\messg \in \Messgs$ would be sent), and a receiver's behavior by a pure strategy $\Rpure \in \States^\Messgs$ which does the opposite.
A play in such a game is illustrated in Figure~\ref{fig:sim-max-illustration}.

>>>>

Formally, a sim-max game consists of a set of states $\States$, a set of messages $\Messgs$ typically with much
fewer messages than states, a probability distribution $\Pr \in \Delta(\States)$ such that
$\Pr(\state)$ gives the probability that state $\state$ occurs, a similarity metric\footnote{A
  metric is a function of distance between any two points in a given space. It should satisfy
  certain axioms that ensure behavior that one would intuitively expect from the words
  ``similarity'' and ``distance'' alone, but these details do not matter for the purposes of
  this paper.}
  % : similarity should always be non-negative, zero only for the distance
  % between an element and itself, symmetric, and satisfy the triangle inequality that
  % $\similarity(x,z) \le \similarity(x,y) + \similarity(y,z)$
on states $\similarity \mycolon \States \times \States \rightarrow \mathds{R}$ such that
$\similarity(\mystate{1}, \mystate{2})$ is the (perceptual) similarity between $\mystate{1}$
and $\mystate{2}$, and a utility function $\Utils \mycolon \States \times \States \rightarrow
\mathds{R}$ such that $\Utils(\mystate{1}, \mystate{2})$ is the payoff for sender and receiver
for a play with actual state $\mystate{1}$ and receiver interpretation $\mystate{2}$. We
identify the receiver's acts with the states of the world, so that the game is one of guessing
the actual state, so to speak. The utility function should be a monotonically increasing
function of similarity.
A sender's behavior can be represented by a pure strategy $\Spure \in \Messgs^\States$, which deterministically defines which message would be used for each state, a mixed strategy $\Smixed \in \Delta(\Messgs^\States)$, which characterizes a probability distribution over pure strategies, or a behavioral strategy $\Sstrat \in \Delta(\Messgs)^\States$, which defines the \emph{probability} that a given message would be used for each state.
The analogous happens for the receiver's behavior.
A play in such a game with behavioral strategies is illustrated in Figure~\ref{fig:sim-max-illustration}.

@@

  \caption{A round of play in a sim-max game with behavioral strategies: Nature (N) chooses a state $\mystate{1}$ with probability $\Pr(\mystate{1})$; a sender (S) selects a message $\messg$ with probability $\Sstrat(\messg \probbar \mystate{1})$; a receiver (R) selects a state $\mystate{2}$ with probability $\Rstrat(\mystate{2} \probbar \messg)$. Payoff for both sender and receiver is given by $\Utils(\mystate{1}, \mystate{2})$.}
   %which is typically proportional to state similarity $\similarity(\mystate{1}, \mystate{2})$.}
  \label{fig:sim-max-illustration}
\end{figure}
